Making all equalities equal

### 2021-12-13 paper.lagda.tex
added few things in the code
added private variable

\usepackage{newunicodechar}
\newunicodechar{∋}{$\ni$}
% \newunicodechar{·}{$\cdot$}
\newunicodechar{⊢}{$\vdash$}
\newunicodechar{⋆}{${}^\star$}
\newunicodechar{Π}{$\Pi$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{ƛ}{$\lambdabar$}
\newunicodechar{∅}{$\emptyset$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ϕ}{$\Phi$}
\newunicodechar{ψ}{$\Psi$}
\newunicodechar{ρ}{$\rho$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{σ}{$\sigma$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{∥}{$\parallel$}
\newunicodechar{Λ}{$\Lambda$}
\newunicodechar{₁}{$~_0$}
\newunicodechar{₁}{$~_1$}
\newunicodechar{₂}{$~_2$}
\newunicodechar{₃}{$~_3$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{Θ}{$\Theta$}
\newunicodechar{∘}{$\circ$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{⊧}{$\models$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{η}{$\eta$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{ξ}{$\xi$}
\newunicodechar{ℕ}{$\mathbb{N}$}
\newunicodechar{ᶜ}{${}^c$}
\newunicodechar{Φ}{$\Phi$}
\newunicodechar{Ψ}{$\Psi$}
\newunicodechar{⊤}{$\top$}
\newunicodechar{≐}{$\doteq$}
\newunicodechar{≣}{$\triangleq$}
\newunicodechar{≃}{$\simeq$}
\newunicodechar{≅}{$\cong$}
\newunicodechar{∙}{$\bullet$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{ℚ}{$\Q$}
\newunicodechar{ℤ}{$\Z$}
\newunicodechar{⦃}{$\{$}
\newunicodechar{⦄}{$\}$}
% \newunicodechar{}{$$}

@@

  record IsEquality (_≣_ : ≣-Type) : Set (ℓ-suc (ℓ-max a ℓ)) where
    constructor eq
    field
      ≣-≡-≡ : ∀ {x y} → let
        x≡y : Type ℓ₁
        x≡y = x ≡ y

@@

    ≡-≡-≣ : {x y : A} → let
      x≡y : Type (ℓ-max a ℓ)
      x≡y = x ≡ y
      x≣y = x ≣ y
      in x≡y ≡ x≣y
    ≡-≡-≣ = sym ≣-≡-≡

@@

\begin{code}
module Equalities {a ℓ} {A : Set a} where
  private
    ≣-Type' = ≣-Type {a} {ℓ} {A}
    ℓ₁ = ℓ-max a ℓ
\end{code}

@@

\begin{code}
    record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
      constructor eq
      field
        ≣-≡-≡ : ∀ {x y} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
\end{code}

@@

      ≡-≡-≣ : {x y : A} → let
        x≡y : Type ℓ₁
        x≡y = x ≡₁ y
        x≣y = x ≣ y
        in x≡y ≡ x≣y
      ≡-≡-≣ = sym ≣-≡-≡

@@

      eqsEqual₂ : ∀ {x y} → let
        x≣₁y : Type ℓ₁
        x≣₁y = x ≡₁ y

@@

      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
        constructor eq
        field
          ≣-≡-≡ : ∀ {x y} → let
            x≡y : Type ℓ₁
            x≡y = x ≡₁ y

@@

        ≡-≡-≣ : {x y : A} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y
        ≡-≡-≣ = let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = IsEquality.≣-≡-≡ eq₁
          α₃ = IsEquality.≡-≡-≣ ≣-isEquality
          in transport α₁ (α₂ ∙ α₃)

@@

        instance
          ≡₂-Equality₃ : IsEquality₃ _≡₂_
          ≡₂-Equality₃ = eq α
            where
              open IsEquality eq₃
              α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
              α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ (eqC _≡₂_)))

>>>>

\usepackage{newunicodechar}
\newunicodechar{∋}{$\ni$}
% \newunicodechar{·}{$\cdot$}
\newunicodechar{⊢}{$\vdash$}
\newunicodechar{⋆}{${}^\star$}
\newunicodechar{Π}{$\Pi$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{ƛ}{$\lambdabar$}
\newunicodechar{∅}{$\emptyset$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ϕ}{$\Phi$}
\newunicodechar{ψ}{$\Psi$}
\newunicodechar{ρ}{$\rho$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{σ}{$\sigma$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{∥}{$\parallel$}
\newunicodechar{Λ}{$\Lambda$}
\newunicodechar{₀}{$~_0$}
\newunicodechar{₁}{$~_1$}
\newunicodechar{₂}{$~_2$}
\newunicodechar{₃}{$~_3$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{Θ}{$\Theta$}
\newunicodechar{∘}{$\circ$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{⊧}{$\models$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{η}{$\eta$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{ξ}{$\xi$}
\newunicodechar{ℕ}{$\mathbb{N}$}
\newunicodechar{ᶜ}{${}^c$}
\newunicodechar{Φ}{$\Phi$}
\newunicodechar{Ψ}{$\Psi$}
\newunicodechar{⊤}{$\top$}
\newunicodechar{≐}{$\doteq$}
\newunicodechar{≣}{$\triangleq$}
\newunicodechar{≃}{$\simeq$}
\newunicodechar{≅}{$\cong$}
\newunicodechar{∙}{$\bullet$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{ℚ}{$\Q$}
\newunicodechar{ℤ}{$\Z$}
\newunicodechar{⦃}{$\{$}
\newunicodechar{⦄}{$\}$}
% \newunicodechar{}{$$}

@@

  record IsEquality (_≣_ : ≣-Type) : Set (ℓ-suc (ℓ-max a ℓ)) where
    constructor eq
    field
      ≣-≡-≡ : let
        x≡y : Type ℓ₁
        x≡y = x ≡ y

@@

    ≡-≡-≣ : let
      x≡y : Type (ℓ-max a ℓ)
      x≡y = x ≡ y
      x≣y = x ≣ y
      in x≡y ≡ x≣y
    ≡-≡-≣ = sym ≣-≡-≡

@@

\begin{code}
module Equalities {a ℓ} {A : Set a} where
  private
    ≣-Type' = ≣-Type {a} {ℓ} {A}
    ℓ₁ = ℓ-max a ℓ

  private variable
    x y z : A
\end{code}

@@

\begin{code}
    record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
      constructor eq
      field
        ≣-≡-≡ : let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
\end{code}

@@

      ≡-≡-≣ : let
        x≡y : Type ℓ₁
        x≡y = x ≡₁ y
        x≣y = x ≣ y
        in x≡y ≡ x≣y
      ≡-≡-≣ = sym ≣-≡-≡

@@

\begin{code}
      eqsEqual₂ : let
        x≣₁y : Type ℓ₁
        x≣₁y = x ≡₁ y

@@

      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
        constructor eq
        field
          ≣-≡-≡ : let
            x≡y : Type ℓ₁
            x≡y = x ≡₁ y

@@

        ≡-≡-≣ : let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y
        ≡-≡-≣ = let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = IsEquality.≣-≡-≡ eq₁
          α₃ = IsEquality.≡-≡-≣ ≣-isEquality
          in transport α₁ (α₂ ∙ α₃)

@@

        instance
          ≡₂-Equality₃ : IsEquality₃ _≡₂_
          ≡₂-Equality₃ = eq α
            where
              open IsEquality eq₃
              α : (x ≡₂ y) ≡₃ (x ≡₁ y)
              α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ (eqC _≡₂_)))
